Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-24 data_appendix_all_years.Rmd
commit

```{r combine household datasets}
all_years <- hh_2005 %>% 
  rbind(hh_2005, hh_2006, hh_2007, hh_2011, hh_2012)

@@

```{r creating summary statistics}

export_summary_table(dfSummary(total_children))

@@

```{r regression variable specifications}
reg_data <- total_subset %>%
  mutate(lny = log(income))
```

@@

model_simple <- lm(assist ~ floods + droughts, data = reg_data)
summary(model_simple)
model_all <- lm(assist ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data)
summary(model_all)
model_register <- lm(register ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data)
summary(model_register)

@@

@@

>>>>

```{r combine household datasets}
all_years <- hh_2005 %>% 
  rbind(hh_2005, hh_2006, hh_2007, hh_2011, hh_2012) %>%

@@

{r creating summary statistics}
export_summary_table(dfSummary(total_subset))

install.packages("devtools")
devtools::install_github("ewenharrison/finalfit")
library(finalfit)
library(dplyr)

```{r regression variable specifications}
total_subset %>%
  mutate(ln_income = log(income))
reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year))

@@

@@

#model_simple <- lm(assist ~ floods + droughts + year, data = reg_data)
#summary(model_simple)
#model_assist <- lm(assist ~ floods + droughts + age + sex + income + hhhead_educ + female_hhhead + year, data = reg_data)
#summary(model_assist)
model_register <- lm(register ~ floods + droughts + age + sex + income + hhhead_educ + female_hhhead + year, data = reg_data)
summary(model_register)

@@

```{r generate regression table, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist, model_register), 
               title = "Full sample regression results", 
               label = "fullResults",
               header = F,
               keep = c("floods", "droughts"))
```

@@

rural <- subset(reg_data, urb_rur == 2, select = c("hh_id", "id", "age", "sex", "literacy", "dept", "urb_rur", "income", "assist", "register", "floods", "droughts", "year", "job", "tasks", "num_children", "female_hhhead", "hhhead_literacy", "hhhead_educ", "year_factor"))

model_assist_r <- lm(assist ~ floods + droughts + age + sex + income + hhhead_educ + female_hhhead + urb_rur + year, data = reg_data)
summary(model_assist_r)
model_register_r <- lm(register ~ floods + droughts + age + sex + income + hhhead_educ + female_hhhead + urb_rur + year, data = reg_data)
summary(model_register_r)
